---
title: "Scenario_test(6)"
output: pdf_document
---

beta: c(2,0.5,rep(0,2),1,rep(0,3))
missing: postive
```{r,echo=FALSE}
load("beta2_missing_positive.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
}
```

\pagebreak


beta: c(2,0.5,rep(0,2),1,rep(0,3))
missing: xy
```{r,echo=FALSE}
load("beta2_missing_xy.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
}
```

\pagebreak

beta: c(2,0.5,rep(0,2),1,rep(0,3))
missing: exp
```{r,echo=FALSE}
load("beta2_missing_exp.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
}
```




\pagebreak


beta: c(3,1.5,rep(0,2),2,rep(0,3))
missing: postive
```{r,echo=FALSE}
load("beta3_missing_positive.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
}
```

\pagebreak


beta: c(3,1.5,rep(0,2),2,rep(0,3))
missing: xy
```{r,echo=FALSE}
load("beta3_missing_xy.Rdata")
```




```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
}
```

\pagebreak

beta: c(3,1.5,rep(0,2),2,rep(0,3))
missing: exp
```{r,echo=FALSE}
load("beta3_missing_exp.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
}
```

\pagebreak