---
title: "Scenario_test(5) SCAD MCP lambda by cross-validation"
output: pdf_document
---

beta: c(2,0.5,rep(0,2),1,rep(0,3))

n: 100

```{r,echo=FALSE}
load("Scenario_beta_2_n_100.Rdata")
```

```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

beta: c(2,0.5,rep(0,2),1,rep(0,3))

n: 300

```{r,echo=FALSE}
load("Scenario_beta_2_n_300.Rdata")
```

```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

beta: c(3,1.5,rep(0,2),2,rep(0,3))

n: 100

```{r,echo=FALSE}
load("Scenario_beta_3_n_100.Rdata")
```

```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

beta: c(3,1.5,rep(0,2),2,rep(0,3))

n: 300

```{r,echo=FALSE}
load("Scenario_beta_3_n_300.Rdata")
```

```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak


beta: c(3,1.5,rep(0,2),2,rep(0,3))

n: 500

```{r,echo=FALSE}
load("Scenario_beta_3_n_500.Rdata")
```

```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```

Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

