---
title: "Scenario_test(6)"
output:
    pdf_document:
        includes:
            in_header: header.tex
---

beta: c(2,0.5,rep(0,2),1,rep(0,3))
missing: xy
postion: 2
```{r,echo=FALSE}
load("beta2_xy_position_2.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```


Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

beta: c(2,0.5,rep(0,2),1,rep(0,3))
missing: xy
postion: 3
```{r,echo=FALSE}
load("beta2_xy_position_3.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```



Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak


beta: c(2,0.5,rep(0,2),1,rep(0,3))
missing: xy
postion: 8
```{r,echo=FALSE}
load("beta2_xy_position_8.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```



Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

beta: c(3,1.5,rep(0,2),2,rep(0,3))
missing: xy
postion: 2
```{r,echo=FALSE}
load("beta3_xy_position_2.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```



Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

beta: c(3,1.5,rep(0,2),2,rep(0,3))
missing: xy
postion: 3
```{r,echo=FALSE}
load("beta3_xy_position_3.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```



Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```

\pagebreak

beta: c(3,1.5,rep(0,2),2,rep(0,3))
missing: xy
postion: 8
```{r,echo=FALSE}
load("beta3_xy_position_8.Rdata")
```


```{r,echo=FALSE}
table_list <- table_res1$result_list
for(i in 1:length(table_list)){
  print(names(table_list)[i])
  print(round(table_list[[i]],3))
}
```



Difference between estimation and true beta value

```{r,echo=FALSE}
diff_list <- table_res1$beta_diff
for(i in 1:length(diff_list)){
  print(names(diff_list)[i])
  print(round(diff_list[[i]],3))
  print("the mean bias is:")
  print(round(colMeans(diff_list[[i]]),3))
}
```
